Extending K-Means Clustering with Ptolemy’s Inequality \thanks{This work is partly funded by DFG grant No. 454630593: EPIX – Efficient Ptolemaic Indexing.}

### 2025-02-27 paper/content/alg_elkan2.tex
fix inexact usage of the parameter in argmin

\begin{algorithm}
	\caption{Elkan's Algorithm}
	\label{alg:elkan}
	\begin{algorithmic}
		\State \textbf{Initialization:} Initialize all cluster centers. For each point $x_i$ and each center $c_j$, set the lower bound $l(x_i,c_j)$ and the upper bound $u(x_i)$. Assign each $x_i$ to the nearest cluster $C_j$ such that $c(x_i) = \argmin_j d(x_i, c_j)$, utilizing that
		$ d(c_j, c_m) \geq 2d(x_i, c_j) \Rightarrow d(x_i, c_m) \geq d(x_i, c_j) $
		to minimize distance calculations. Set $r(x_i) = \text{true}$ for all points.

>>>>

\begin{algorithm}[h]
	\caption{Elkan's Algorithm}
	\label{alg:elkan}
	\begin{algorithmic}
		\State \textbf{Initialization:} Initialize all cluster centers. For each point $x_i$ and each center $c_j$, set the lower bound $l(x_i,c_j)$ and the upper bound $u(x_i)$. Assign each $x_i$ to the nearest cluster $C_j$ such that $c(x_i) = \argmin_{j'} d(x_i, c_{j'})$, utilizing that
		$ d(c_j, c_m) \geq 2d(x_i, c_j) \Rightarrow d(x_i, c_m) \geq d(x_i, c_j) $
		to minimize distance calculations. Set $r(x_i) = \text{true}$ for all points.
